Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-24 paper/ijcai/paper.tex
abstract+intro update

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to evaluate the effects of combining \ds{} with \sfl{}. We suspect
that several highly suspicious components---often involved in failing,
but seldom in passing test runs---may be unrelated to the bug. With
the aforementioned combination, such components could be located and
their suspiciousness reduced.  This study also discusses the practical
impact of the \ds{} key limitation---the risk of missing faulty
statements. Results indicate that \ds{} misses faulty statements in
 9\%\comments{(23 misses)} of the \numFaults{} cases and that
the \ds{}-\sfl{} combination, coined as Tandem-SL, improves
the diagnostic accuracy of the diagnostic report in \avgImprov\ on average
for 51\% of the cases. To sum,
we found that the \ds{}-\sfl{} combination was practical and effective
and encourage new \sfl{} techniques to be evaluated against that
optimization.
\end{abstract}

@@

Given the importance of fault localization, this paper revisits the
problem of assessing the effectiveness of combining \ds{} and \sfl{},
addressing the key issues of prior work. We conducted a comprehensive
study involving \numFaults{} faults from \numPrograms{} different
programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluate fault localization research. Results show that \ds{} misses
faulty statements in 9\%\comments{(23 misses)} of the \numFaults{}
faults analyzed. Furthermore, we found that the combination of the two
approaches improves fault localization in 51\% of the cases with an
average improvement of \avgImprov. To sum, results indicate that the
risk of applying the technique is relatively low for the positive
impact it may bring and the tool implementing the technique works
out-of-the-box, \ie{}, it puts no requirements on the running
environment, subject programs it can be used, and requires no special
setup.

@@

Model-based diagnosis is a well-known approach that has been proposed by the
DX community, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
of model-based diagnosis to localize software faults have demonstrated that it
can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,Mayer:2008:EMM:1642931.1642950}.

Dynamic slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
static slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
is an instance of Model-based software diagnosis that
has been shown useful in automated software debugging where the region
of interest is restricted to what can be reached from failing
tests. Several dynamic slicing techniques exist. This paper uses
Critical Slicing (\cs{})~\cite{DeMillo:1996:CSS:229000.226310} for its
simplicity/generality. Critical Slicing
prescribes a black-box language-semantics-agnostic recipe to computing
executable slices. Critical Slicing simplifies the original
program such that the resulting program preserves critical
observations, such as assertion violations. More precisely, the
simplification mechanism consists of deleting statements on the
original program and checking if the output of the original and
modified program are the same.

@@

It is worth noting that this is not a problem that afflicts only CS;
\emph{all} purely dynamic slicing techniques manifest this
problem~\cite{Lin:2018:BDE:3238147.3238163}. To mitigate the issue in
CS, it is necessary to make oracles more specific. For that, our
approach was to use as the slicing criterion the stack trace
associated with the test failure. That decision increases the chances
that the sliced program will follow a path to the error similar to
that followed by the original program.
There are faults whose outputs
may slightly differ from one execution to another. For example,
exceptions including memory addresses identifiers, which change on
each execution. For these cases, it was developed a mechanism to compare the
rest of the output ignoring the identifier of the memory address.

@@

\subsection{Techniques}
One important independent variable for this study is the scope of
dynamic slicing. Slicing the entire code would be unacceptably
expensive as Critical Slicing needs to re-compile the affected file at
every iteration, \ie{}, after deleting statements and before checking
the oracle (see Section~\ref{sec:slicing}). We control the scope of
slicing through the variable $k$, which denotes the number of distinct
files that dynamic slicing will minimize. In this study, we used $5$ and
$10$ as the values of $k$, following the same values as in previous fault
localiztion studies~\cite{ang-perez-van-deursen-rui-2017}.
The $k$ files for minimization are selected
from the \sfl{} ranking as follows. First, we build a rank of files by
determining, for each ranked statement, the file that declares
it. Then, we select the top $k$ distinct files from such file ranking.

@@

        \lang{}            & 100.0 & 96.9\\
        \cmath{}           & 89.4 & 95.2\\
        %\closure{}          &  & \\
		\chart{}			& 76.9 & 84.6 \\
        \jtime{}            & 81.5 & 85.2\\
        \mockito{}          & 71.1 & 78.9\\

@@

\begin{table}[h!]
	\small
	\setlength{\tabcolsep}{3pt}
	\centering
	  \begin{tabular}{l|rr|rr}
		 \toprule
       & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
		 Project        &   \sfl{}   & \comb &   \sfl{}   & \comb\\
		\midrule
		 \lang{}         &   84.6   & 100.0 & 84.6 & 96.9  \\
		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 \\
		\chart{}           & {\cellcolor{Gray} 84.6} & {\cellcolor{Gray}76.9} & {\cellcolor{Gray}92.3} & {\cellcolor{Gray}84.6}\\
		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2\\
		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9\\   \midrule
		Total         & 79.6 & 87.3 & 83.5 & 91.2\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the faulty-statements is in the \sfl{}$^{k}$ and \combpar{k} report}
  \label{table:fsws}
\end{table}

>>>>

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to evaluate the effects of combining \ds{} with \sfl{}. We suspect
that several highly suspicious components---often involved in failing,
but seldom in passing test runs---may be unrelated to the bug. With
the aforementioned combination, such components could be located and
their suspiciousness reduced.  This study also discusses the practical
impact of the \ds{} key limitation---the risk of missing faulty
statements. Results indicate that \ds{} misses faulty statements in
 $9\%$\comments{($23$ misses)} of the $\numFaults{}$ cases and that
the \ds{}-\sfl{} combination, coined as Tandem-SL, improves 
the diagnostic accuracy up to $73.7\%$ (\avgImprov\ on average)\Sof{Calculei
mal a média antes. A melhoria média para o top-5 é 9.6\% e a máxima
melhoria que a técnica atingiu foi de 96.7\%. Eu reportei aqui no abstract para o
top-10 porque a \% de melhoria é maior. Se vocês acharem que é mais vantajoso
reportar os valores do top-10, avisem. Podemos reportar ambas. Atenção, só considero
os casos em que pelo menos uma das variantes obteve melhoria}. To sum,
we found that the \ds{}-\sfl{} combination was practical and effective
and encourage new \sfl{} techniques to be evaluated against that
optimization.
\end{abstract}

@@

Given the importance of fault localization, this paper revisits the
problem of assessing the effectiveness of combining \ds{} and \sfl{},
addressing the key issues of prior work. We conducted a comprehensive
study involving \numFaults{} faults from \numPrograms{} different
programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluate fault localization research. Results show that \ds{} misses
faulty statements in $9\%$\comments{(23 misses)} of the \numFaults{}
faults analyzed. Furthermore, we found that the combination of the two
approaches may improve fault localization up to $73.7\%$ (\avgImprov\ on average).
 To sum, results indicate that the
risk of applying the technique is relatively low for the positive
impact it may bring; and, the tool implementing the technique works
out-of-the-box, \ie{}, it puts no requirements on the running
environment, subject programs it can be used, and requires no special
setup.

@@

Model-based software diagnosis has been

model-based software debugging, from the DX community, has been shown to be similar to slicing Mayer and Stumptner, 2008; Wotawa and Nica; etc. Having said that, not many inter- esting techniques having been pursued because of scalability. We have achieved it with a type of program slicing — critical slicing.

% Program slicing is a program understanding technique to identify the
% relevant parts of the program with respect to given points of
% interest.
\Sof{MBSD connection review please}
Dynamic slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
static slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
is an instance of Model-based software diagnosis that
has been shown useful in automated software debugging where the region
of interest is restricted to what can be reached from failing
tests. Several dynamic slicing techniques exist. This paper uses
Critical Slicing (\cs{})~\cite{DeMillo:1996:CSS:229000.226310} for its
simplicity/generality. Critical Slicing
prescribes a black-box language-semantics-agnostic recipe to computing
executable slices. Critical Slicing simplifies the original
program such that the resulting program preserves critical
observations, such as assertion violations. More precisely, the
simplification mechanism consists of deleting statements on the
original program and checking if the output of the original and
modified program are the same.

@@

It is worth noting that this is not a problem that afflicts only CS;
\emph{all} purely dynamic slicing techniques manifest this
problem~\cite{Lin:2018:BDE:3238147.3238163}. To mitigate the issue in
CS, it is necessary to make oracles more specific. For that, our
approach was to use as the slicing criterion the stack trace
associated with the test failure. That decision increases the chances
that the sliced program will follow a path to the error similar to
that followed by the original program. \Sof{Added oracle generalization example}
There are faults whose outputs 
may slightly differ from one execution to another. For example, 
exceptions including memory addresses identifiers, which change on 
each execution. For these cases, it was developed a mechanism to compare the
rest of the output ignoring the identifier of the memory address.

@@

\subsection{Techniques}
One important independent variable for this study is the scope of
dynamic slicing. Slicing the entire code would be unacceptably
expensive as Critical Slicing needs to re-compile the affected file at
every iteration, \ie{}, after deleting statements and before checking
the oracle (see Section~\ref{sec:slicing}). We control the scope of
slicing through the variable $k$, which denotes the number of distinct
files that dynamic slicing will minimize. In this study, we used 5 and
10 as the values of $k$. The $k$ files for minimization are selected
from the \sfl{} ranking as follows. First, we build a rank of files by
determining, for each ranked statement, the file that declares
it. Then, we select the top $k$ distinct files from such file ranking.
\Rui{we should say that k follows from typical SFL metrics (top k)}

@@

        \lang{}            & 100 & 96.9\\
        \cmath{}           & 89.4 & 95.2\\
        %\closure{}          &  & \\
		\chart{}			& 76.9 & 84.6 \\
        \jtime{}            & 81.5 & 85.2\\
        \mockito{}          & 71.1 & 78.9\\

@@

\begin{table*}[t!]
	\small
	% \setlength{\tabcolsep}{3pt}
	\centering
	  \begin{tabular}{l|cc|cc|c}
		\toprule
		 Project        &   \sfl{}$^{5}$   & \combpar{5}
		 				&   \sfl{}$^{10}$   & \combpar{10}& \# Faults      \\
		\midrule
		 \lang{}         &   84.6   & 100 & 84.6 & 96.9 & 65      \\
		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 & 104  \\   
		\chart{}           & 84.6 & 76.9 & 92.3 & 84.6 & 26  \\
		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2 & 27  \\   
		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9 & 38  \\   \midrule
		Total         & 79.6 & 87.3 & 83.5 & 91.2 & 260  \\  
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the faulty-statements is in the \sfl{}$^{k}$ and \combpar{k} report}
  \label{table:fsws}
\end{table*}
